Software Ticket Quality

### 2017-10-17 proposal/mprop.tex
Added the 9th paper

@@

\textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:
\begin{itemize}
  \item \textbf{What were the goals?}
  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}

>>>>

\textbf{Software Quality \- The Elusive Target}\cite{kitchenham1996software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to determine what makes for a good quality
    software project, as well as who are the people in charge of this aspect
    and how should they approach achieving it.
  \item \textbf{What was the method?}
    They tried to define quality in software projects and analyze techniques that 
    measure such quality by looking at other models proposed in different other  
    papers (e.g.\ McCall's quality model, ISO 9126).
  \item \textbf{What did they learn?}
    They learned that quality is very hard to define and there are various 
    factors which need to be taken into consideration, such as the business
    model of the company, the type of the software project (e.g.\ safety
    critical, financial) or the actors which are involved and how they
    coordinate the software activities.
  \item \textbf{Relevance to our work}: this paper is a key paper on software  
    quality and it can prove beneficial in our research by
    giving valuable insights into how software quality can be modeled, thus
    helping us in selecting good quality open source repositories to work with 
    (i.e.\ ticket selection and analysis).
\end{itemize}

@@

\textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
\begin{itemize}
  \item \textbf{What were the goals?}
  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}
